Spatial Reasoning and Data Displays

### 2015-01-27 Paper/Draft1/TestingVisualAptitude.Rnw
Principal component explanation

A principal component analysis (PCA) of the four established visuo-spatial tests reveals that they all share a very strong first component, which explains about \Sexpr{round(summary(pca2)$importance[3,1],2)*100}\% of the total variability.

\comment{You'll have to define the use of PCX still - a quick sentence on the order of the principal components being given by the amount of variance in the data that they explain should do it.}

>>>>

A principal component analysis (PCA) of the four established visuo-spatial tests reveals that they all share a very strong first component, which explains about \Sexpr{round(summary(pca2)$importance[3,1],2)*100}\% of the total variability. Principal components (PC-) are ordered by importance (how much variability in the data they contain), and each principal component is uncorrelated with every other principal component.
